%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Preamble
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%% The uwthesis.sty file relies on the memoir class!
%%%% You should be using the memoir class anyway; it makes life easier:
%%%% http://www.ctan.org/tex-archive/macros/latex/contrib/memoir/
\documentclass[oneside, letterpaper, 12pt, oldfontcommands]{memoir}

%%%% Import uwthesis.sty to get official formatting, then set your variables.
\usepackage{uwthesis}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{longtable}
\usepackage{caption}
\usepackage{multirow}
\usepackage{lineno}
\usepackage{xcolor}
\usepackage[colorlinks=true,allcolors=blue]{hyperref}
\usepackage[capitalise]{cleveref}
%\renewbibmacro*{bbx:savehash}{}
%\addbibresource{references.bib}
\setlrmarginsandblock{1in}{1in}{*}
\setulmarginsandblock{1in}{1in}{*}
\checkandfixthelayout
\setsecnumdepth{paragraph}
\maxtocdepth{subsection}

%\nolinenumbers{}
%\linenumbers

\settitle{Every Flare, Everywhere: Untriggered Searches for Astrophysical Neutrino Transients Using Data From the IceCube Detector}
\setauthor{William Luszczak}
\setdepartment{Physics}
\doctors % or \masters
\setgraddate{2021}
\setdefensedate{19 August 2021} % or whatever format you want

%%%% Members of the Final Oral Committee (FOC)
%%%% Give name, rank, and department
%%%% 
\setfoca{Albrecht Karle}{Professor}{Physics} % <- Your advisor
\setfocb{Keith Bechtol}{Assitant Professor}{Physics}
\setfocc{Ke Fang}{Assistant Professor}{Physics}
\setfocd{Sebastian Heinz}{Professor}{Astronomy}

%%%% Your abstract, used for the UMI abstract and in your front matter
\setabstract{%
  Recent results from the IceCube collaboration regarding the blazar TXS 0506+056 suggest the presence of neutrino flares that are not temporally coincident with a significant corresponding gamma ray flare. Such flares are particularly difficult to identify, as their presence must be inferred from the temporal distribution of neutrino data alone. While previously existing statistical methods fit for only the largest neutrino flare candidate at a particular location, this work introduces an extension to fit for the contributions from multiple flare candidates at once, thereby increasing the sensitivity to sub-threshold neutrino flares. The need for a multiple flare fit is further motivated by the increasing duration of the IceCube data available for analysis. In this work, this "multi-flare" method is applied to data from the IceCube Neutrino Observatory using two different source catalogs to explore emission from candidates similar to TXS 0506+056. This method is additionally used to create a "multi-flare" skymap, describing the temporal variability of IceCube data at every point in the neutrino sky. These results can be used to place further constraints on potential populations of transient neutrino sources, serving as a complement to existing time-integrated and time-dependent methods.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Tell the memoir class to set up lowercase roman for pagination, etc.
\frontmatter

%%%% Uncomment this to create a UMI abstract page.
%%%% If you are submitting electronically, however, this page is unnecessary.
% \theumiabstract

% The title page
\thetitlepage
\clearpage

% The copyright page, if you want to pay the fee and register copyright.
\thecopyrightpage
\cleardoublepage

% These above pages should not be counted, so we reset the counter to 1.
\setcounter{page}{1}

% An abstract may be required by your department.
\section{Abstract}
\uwabstract
\cleardoublepage

% Acknowledgements go here if you want to include them.
\section{Acknowledgements}
This thesis is dedicated to all the people who helped me along the way.

Thank you to my parents, Michael and Janice Luszczak, for loving and supporting me since childhood, as well as for ensuring I had a strong start to my education which has undoubtedly served me well to this day. I will always be impressed by just how good of a start you both gave me to the rest of my life. 

Thank you to my undergraduate research advisor, Ben Monreal, for putting up with me when I was a dumb and useless undergraduate researcher. Despite my uselessness as an undergrad, the opportunities you provided were the start of my growth into the (hopefully slightly less useless) physicist I am today. 

Thank you to my graduate advisor, Albrecht Karle, for providing the resources, direction, guidance, and freedom to foster my scientific growth over the past five years. Additional thanks to Jim Braun, for teaching and guiding me through the development of much of what is presented in this thesis.

More broadly, I am especially thankful for WIPAC and the members of the IceCube collaboration, in particular those who maintain the detector, software, and data for the rest of us to use. I'd like to specifically call out Mike Richman, whose software framework (cSky) was an integral component to making much of this work possible. 

Final thanks to Dan, Bhavna, Krysten, David, and Zain: my friends and classmates who were the best part of undergrad, and who deserve a lot of credit for making the start of my academic career enjoyable. I'd also like to thank Sarah and Austin, who in addition to being valued friends, served as unofficial peer mentors over the past five years of graduate school. 

 

 
\clearpage

% Table of contents
\maxtocdepth{subsection}
\tableofcontents* % the * means that there isn't an entry for the TOC itself
% \clearpage
% \listoffigures  % if you have any figures
% \clearpage
% \listoftables   % if you have any tables

% Tell the memoir class to set up normal pagination, etc. for the main doc
\mainmatter

\include{chapters/Introduction}
\include{chapters/ScienceBackground}
\include{chapters/DetectorDescription}
\include{chapters/Methods}
\include{chapters/CatalogSearches}
\include{chapters/Skymap}
\include{chapters/Outro}
\include{chapters/Stats}

\footnotesize \bibliography{references}{}
\bibliographystyle{unsrt}
\end{document}
